\section{Introduction}

This report describes and gives evidence of many of the issues present in the UCL engineering department based on my experience doing the MSc Mechanical Engineering course 2023-2024. While this report is a long way from exhaustive, it is intended to be used as a reasonably comprehensive source to inform future changes to the running of the course.

For additional context, my undergraduate was in mathematics at the University of Oxford. My experience there is used as a point of comparison throughout this report, although my friends went to a wide range of universities and have had very similar comments. Given that UCL is a top ten university with one league table even ranking it as high as fourth place, this should not be an unreasonable comparison.

I have written this report without a name attached, although there is identifiable information here\footnote{For example I reference a post I wrote on Unitu that I wrote non-anonymously.}, and those in the department would almost certainly know who wrote this from a description of the document alone. I do not care too much about anonymity however as long as it does not influence my grade, and I am perfectly happy for this document to be shared with all interested parties. This includes but is not limited to, the engineering department, the external review board, and the higher level administrators at UCL.

This report has been split into three main sections, reviewing the quality of the resources made available, the handling of coursework, and high level decisions about the course and its administration. The issues with the group design module and academic integrity policy warranted their own subsections and are discussed in section~\ref{sec:ParticularIssues}. While suggestions are given throughout the document, these are collated and presented in section~\ref{sec:Conclusion}. Much of the justification for these is found in the rest of the report and will not be repeated there however.